---
title: "Final Project data cleaning"
author: "Chen Zi Xin"
date: "2023-10-30"
output: html_document
---

## General Data
```{r eval=TRUE, echo=TRUE}
library(tidyverse)
library(ggplot2)

Speed_Dating_Data <- read_csv("Speed Dating Data.csv")

General_Attributes <- Speed_Dating_Data %>% 
  select(attr_o, sinc_o, intel_o, fun_o, amb_o, shar_o)

General_Attributes_long <- General_Attributes %>%
  pivot_longer(cols = everything(), names_to = "Attribute", values_to = "Rating")

ggplot(General_Attributes_long, aes(x = Attribute, y = Rating, fill = Attribute)) +
  geom_boxplot() +
  geom_jitter(position = position_jitter(width = 0.3, height = 0), alpha = 0.5) +
  labs(x = "Attribute", y = "Rating") +
  ggtitle("Distribution of Ratings for General Attributes") +
  scale_fill_discrete(name = "Attribute")
```

## Splitting into Male and Female 

```{r eval=TRUE, echo=TRUE}
library(tidyverse)

Speed_Dating_Data <- read_csv("Speed Dating Data.csv")
Females <- Speed_Dating_Data[Speed_Dating_Data$gender == 1, ]
Males <- Speed_Dating_Data[Speed_Dating_Data$gender == 0, ]
```

##Successful Matches 
```{r eval=TRUE, echo=TRUE}
library(tidyverse)

Speed_Dating_Data <- read_csv("Speed Dating Data.csv")
All_Matches <- Speed_Dating_Data %>% filter(match == 1) %>% select(match, gender, age_o)

# Create a ggplot
ggplot(All_Matches, aes(x = age_o)) +
  geom_bar() +
  labs(title = "Successful Matches by Age", x = "Age", y = "Count") +
  theme_minimal()

```

#MALE DATA 

##Successful Matches 
```{r eval=TRUE, echo=TRUE}
library(tidyverse)

Speed_Dating_Data <- read_csv("Speed Dating Data.csv")
Males <- Speed_Dating_Data[Speed_Dating_Data$gender == 0, ]
Male_Matches <-Males %>% filter(match == 1) %>% select(match)
```

##Age that is most "attractive"
```{r eval=TRUE, echo=TRUE}
library(tidyverse)
Speed_Dating_Data <- read_csv("Speed Dating Data.csv")
Males <- Speed_Dating_Data[Speed_Dating_Data$gender == 0, ]
Male_Matches_Age <-Males %>% filter(match == 1) %>% select(age_o)
```

##Filtering the above average matches 
```{r eval=TRUE, echo=TRUE}
library(dplyr)
library(tidyverse)
Speed_Dating_Data <- read_csv("Speed Dating Data.csv")

Males_Attributes <- Males %>% filter(attr_o >= 5, sinc_o >= 5, intel_o >= 5, fun_o >= 5, amb_o >= 5, shar_o >= 5) %>% filter(match ==1) %>% select(attr_o,sinc_o,intel_o,fun_o,amb_o,shar_o)

```

##Calculating mean of all attributes
```{r eval=TRUE, echo=TRUE}
library(dplyr)

attractive <- Males_Attributes %>% 
summarize(mean_attr_o = mean(attr_o, na.rm = TRUE))
print(attractive)

sincere <- Males_Attributes %>% 
summarize(mean_sinc = mean(sinc_o, na.rm = TRUE))
print(sincere)

intelligent <- Males_Attributes %>% 
summarize(mean_intel = mean(intel_o, na.rm = TRUE))
print(intelligent)

fun <- Males_Attributes %>% 
summarize(mean_fun = mean(fun_o, na.rm = TRUE))
print(fun)

ambitious<- Males_Attributes %>% 
summarize(mean_amb = mean(amb_o, na.rm = TRUE))
print(ambitious)

shared_interests <- Males_Attributes %>% 
summarize(mean_shar = mean(shar_o, na.rm = TRUE))
print(shared_interests)
```

##Plotting Visualisation for Male Attributes (Ranking)

```{r eval=TRUE, echo=TRUE}
library(ggplot2)

Attributes <- c("Attractive", "Sincere", "Intelligent", "Fun", "Ambitious", "Shared Interests")

Scores <- c(7.637963, 7.890741, 7.878704, 7.712037, 7.366667, 7.065741)

Males_Attributes <- data.frame(
     Attribute = Attributes,
    Score = Scores)

ggplot(Males_Attributes, aes(x = Attribute, y = Score)) +
     geom_segment(aes(xend = Attribute, yend = "Attractive"), size = 2, lineend = "round") +
     labs(x = "Attributes", y = "Scores") +
     theme_minimal()
```

#FEMALE DATA 

##Successful Matches 
```{r eval=TRUE, echo=TRUE}
library(tidyverse)

Speed_Dating_Data <- read_csv("Speed Dating Data.csv")
Females <- Speed_Dating_Data[Speed_Dating_Data$gender == 1, ]
Female_Matches <- Females %>% filter(match == 1)%>% select(match)

```

##Age that is most "attractive"
```{r eval=TRUE, echo=TRUE}
library(tidyverse)

Speed_Dating_Data <- read_csv("Speed Dating Data.csv")
Females <- Speed_Dating_Data[Speed_Dating_Data$gender == 1, ]
Female_Matches_Age <- Females %>% filter(match == 1)%>% select(age_o)

```

##Filtering the above average matches 
```{r eval=TRUE, echo=TRUE}
library(dplyr)

Female_Attributes <- Females %>% filter(attr_o >= 5, sinc_o >= 5, intel_o >= 5, fun_o >= 5, amb_o >= 5, shar_o >= 5) %>% filter(match ==1) %>% select(attr_o,sinc_o,intel_o,fun_o,amb_o,shar_o)

```

##Calculating mean of all attributes
```{r eval=TRUE, echo=TRUE}
library(dplyr)

attractive <- Female_Attributes %>% 
summarize(mean_attr_o = mean(attr_o, na.rm = TRUE))
print(attractive)

sincere <- Female_Attributes %>% 
summarize(mean_sinc = mean(sinc_o, na.rm = TRUE))
print(sincere)

intelligent <- Female_Attributes %>% 
summarize(mean_intel = mean(intel_o, na.rm = TRUE))
print(intelligent)

fun <- Female_Attributes %>% 
summarize(mean_fun = mean(fun_o, na.rm = TRUE))
print(fun)

ambitious<- Female_Attributes %>% 
summarize(mean_amb = mean(amb_o, na.rm = TRUE))
print(ambitious)

shared_interests <- Female_Attributes %>% 
summarize(mean_shar = mean(shar_o, na.rm = TRUE))
print(shared_interests)
```

```{r eval=TRUE, echo=TRUE}
library(ggplot2)

Attributes <- c("Attractive", "Sincere", "Intelligent", "Fun", "Ambitious", "Shared Interests")

Scores <- c(7.48768, 8.01232, 8.204312, 7.917864, 7.74538, 7.25462	)

Female_Attributes <- data.frame(
     Attribute = Attributes,
    Score = Scores)

ggplot(Female_Attributes, aes(x = Attribute, y = Score)) +
     geom_segment(aes(xend = Attribute, yend = "Attractive"), size = 2, lineend = "round") +
     labs(x = "Attributes", y = "Scores") +
     theme_minimal()
```

##Comparing Male and Female Data
```{r eval=TRUE, echo=TRUE}
library(tidyverse)
library(readr)
library(ggplot2)

# Assuming 'gender' and 'match' are columns in your data
Speed_Dating_Data <- read_csv("Speed Dating Data.csv")

# Filter and select relevant columns
Successful_Matches <- Speed_Dating_Data %>%
  filter(match == 1) %>%
  select(match, gender)

# Calculate success rates
success_rates <- Successful_Matches %>%
  group_by(gender) %>%
  summarise(success_rate = n() / nrow(Successful_Matches))

# Create a dot plot for success rates
ggplot(success_rates, aes(x = gender, y = success_rate, color = gender)) +
  geom_point(position = position_dodge(width = 0.2), size = 3) +
  labs(x = "Gender",
       y = "Success Rate",
       title = "Dot Plot of Success Rates for Male and Female Matches") +
  theme_minimal()

```

##Comparing Male and Female Data (Attributes)
```{r eval=TRUE, echo=TRUE}
library(tidyverse)
library(ggplot2)

# Sample data or replace it with your actual data
Males_Scores <- c(7.637963, 7.890741, 7.878704, 7.712037, 7.366667, 7.065741)
Female_Scores <- c(7.48768, 8.01232, 8.204312, 7.917864, 7.74538, 7.25462)

Attributes <- c("Attractive", "Sincere", "Intelligent", "Fun", "Ambitious", "Shared Interests")

Gender <- data.frame(
  Gender = rep(c("Male", "Female"), each = length(Males_Scores)),
  Attributes = rep(Attributes, 2),
  Scores = c(Males_Scores, Female_Scores)
)

# Create a ggplot
ggplot(Gender, aes(x = Attributes, y = Scores, fill = Gender)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  labs(x = "Attributes", y = "Scores", fill = "Gender") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

### Career
```{r eval=TRUE, echo=TRUE}
library(tidyverse)
library(ggplot2)

Speed_Dating_Data <- read_csv("Speed Dating Data.csv")

# Filter for successful matches and select the field column
fields_data <- Speed_Dating_Data %>% 
  filter(match == 1) %>% 
  select(field)

# Count the occurrences of each field
field_counts <- table(fields_data$field)

# Create a dataframe from the table
field_counts_df <- data.frame(Field = names(field_counts), Count = as.numeric(field_counts))

# Order the dataframe by count in descending order
field_counts_df <- field_counts_df %>% arrange(desc(Count))

# Select the top 30 fields
top_30_fields <- head(field_counts_df, 30)

# Create a bar plot with expanded horizontal length
ggplot(top_30_fields, aes(x = reorder(Field, -Count), y = Count)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Top 30 Most Popular Fields of Study",
       x = "Field of Study",
       y = "Number of Successful Matches") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
